  ---
title: "Capstone TCD project note II"
author: "Suprasanna Pradhan"
date: "26 September 2019"
output:
  html_document: default
  word_document: default
---

```{r}
library(caret)
library(class)
library(devtools)
library(e1071)
library(ggplot2)
library(Hmisc)
library(klaR)
library(MASS)
library(nnet)
library(plyr)
library(pROC)
library(psych)
library(scatterplot3d)
library(SDMTools)
library(dplyr)
library(ElemStatLearn)
library(rpart)
library(rpart.plot)
library(randomForest)
library(neuralnet)
```

#Recap of Project note 1
.	In the data set earlier we found it consists 30000 observations with 25 variables.
.	The categorical data value like Sex , martial status and education  has changed to numeric value . 
.	We have realized that 22.1 % percent defaulter and 77.9% are not default cases 
.	Default category whereas male customer are 9.6% and female category shows 12.5% . 
.	University level - graduate or PG is more into default side 
.	Married customers somehow leaning to tend defaulter 
.	Average age of 25 to 30 is the highest risk . 
.	We have also checked the multicollinearity problems is existed In the data set . . pay status categorical variables are dependent on each other and impact of REPAY_ SEP to REPAY_APR variables to default. Payment DEFAULT is high. 
.	We have also created some dummy variables like ratio of the payment for each month SEP to APR and balance amount month wise from SEP to APR . 

#Suppllimantry Over view of EDA
We have been checking here the relationship of paid amount SEP to APR and balance amount(( billed  outstanding amount - paid amount ) we assumed that bank is keep on adding the preceding month balance to current month ) 


# importing the data from Note 1
Ratio is alrady added in the data set .
```{r}
library(readxl)
#Importing Data set
setwd("C:/Users/SuprasannaPradhan/Documents/My Files/Great Lakes Projects/Capstone Project TCD")
bank_data_2nd=read.csv("bank_data_new.csv")
bank_data_2=read.csv("taiwan_bank3.csv")
names(bank_data_2)

```

##Finding outliers and NA values 
```{r}
bank_data_n1 <- subset(bank_data_2nd, select = -c(1:2))
bank_data1 <- cbind(bank_data_n1,bank_data_2[21:26])
str(bank_data1)
summary(bank_data1)

```   

we got here few variables are having outliers ,found almost all continours frequancy based variable are having outliers but variables are having extem outlier values these are limit balance, BILL_AMT_JUL ,PAID_AMT_AUG,balance_JUL 
Dummy ration created from SEP to APR shows lot of NA and inf values.

#Handling of Ratio paybill amount 
Ratio Pay Amount Bill Amount Negative/NaN number 1. If Bill Amount =0 : Then convert Ratio to positive 2. Impute NaN to 1 (Higher the ratio, lesser the chance of Default) 
```{r}
bank_data1[is.na(bank_data1)] <- 0
sum(is.na(bank_data1))
bank_data1$RATIO_SEP=ifelse(bank_data1$RATIO_SEP<=100,0,1) 
bank_data1$RATIO_AUG=ifelse(bank_data1$RATIO_AUG<=100,0,1)
bank_data1$RATIO_JUL=ifelse(bank_data1$RATIO_JUL<=100,0,1)
bank_data1$RATIO_JUN=ifelse(bank_data1$RATIO_JUN<=100,0,1)
bank_data1$RATIO_MAY=ifelse(bank_data1$RATIO_MAY<=100,0,1)
bank_data1$RATIO_APR=ifelse(bank_data1$RATIO_APR<=100,0,1)
str(bank_data1[25:30])
View(bank_data1)


```


```{r}
#write.csv(bank_data1, file = 'bank_data1.csv')
table(bank_data1$RATIO_SEP)
table(bank_data1$RATIO_AUG)
table(bank_data1$RATIO_JUL)
table(bank_data1$RATIO_JUN)
table(bank_data1$RATIO_MAY)
table(bank_data1$RATIO_APR)

```



```{r}
bank_data_bp <- subset(bank_data1,select = -c(2,3,4,24:30))
names(bank_data_bp)
boxplot(bank_data_bp)
```
Ratio culmun we are not checking the outliers becuse it values are very low .it is show us the size of the amount ahs been paid for each month ,hence we not incluing these variabels for outlier checking 
```{r}
#Capping vairbale outlieres
capOutlier <- function(x){
   qnt <- quantile(x, probs=c(.25, .75), na.rm = T)
   caps <- quantile(x, probs=c(.05, .95), na.rm = T)
   H <- 1.5 * IQR(x, na.rm = T)
   x[x < (qnt[1] - H)] <- caps[1]
   x[x > (qnt[2] + H)] <- caps[2]
   return(x)
}
bank_data1$LIMIT_BAL=capOutlier(bank_data1$LIMIT_BAL)
bank_data1$BILL_AMT_SEP=capOutlier(bank_data1$BILL_AMT_SEP)
bank_data1$BILL_AMT_AUG=capOutlier(bank_data1$BILL_AMT_AUG)
bank_data1$BILL_AMT_JUL=capOutlier(bank_data1$BILL_AMT_JUL)
bank_data1$BILL_AMT_JUN=capOutlier(bank_data1$BILL_AMT_JUN)
bank_data1$BILL_AMT_MAY=capOutlier(bank_data1$BILL_AMT_MAY)
bank_data1$BILL_AMT_APR=capOutlier(bank_data1$BILL_AMT_APR)
bank_data1$PAID_AMT_SEP=capOutlier(bank_data1$PAID_AMT_SEP)
bank_data1$PAID_AMT_AUG=capOutlier(bank_data1$PAID_AMT_AUG)
bank_data1$PAID_AMT_JUL=capOutlier(bank_data1$PAID_AMT_JUL)
bank_data1$PAID_AMT_JUN=capOutlier(bank_data1$PAID_AMT_JUN)
bank_data1$PAID_AMT_MAY=capOutlier(bank_data1$PAID_AMT_MAY)
bank_data1$PAID_AMT_APR=capOutlier(bank_data1$PAID_AMT_APR)
bank_data1$balance_SEP=capOutlier(bank_data1$balance_SEP)
bank_data1$balance_AUG=capOutlier(bank_data1$balance_AUG)
bank_data1$balance_JUL=capOutlier(bank_data1$balance_JUL)
bank_data1$balance_JUN=capOutlier(bank_data1$balance_JUN)
bank_data1$balance_MAY=capOutlier(bank_data1$balance_MAY)
bank_data1$balance_APR=capOutlier(bank_data1$balance_APR)


```

#Cappped outliers for these variables

```{r}
bank_data_bp1 <- subset(bank_data1,select = -c(2,3,4,24:32))
boxplot(bank_data_bp1)
```



```{r}
##Checking Data ##
colSums(is.na(bank_data1))
```

All NA are shown in the dummy variable of ratio, we understand this values are occured due to the paid amount by the cutomser are not paid as the outstanding bill amount shown each month or very less againg of outstandin billed amount .So we would be keeping in as it is , if needed in future we will make them zero .


#let us chekc the REPAY variables and clsifiy them , timely paid and delayed in payeemnt 


According to the description, this REPAY_SEP TO REPAy_APR is a set of categorical variables with the levels:-2 is No consumption; -1 is  Paid in full; 0 is The use of revolving credit; 1 is payment delay for one month; 2 is payment delay for two months; . . .; . 8=payment delay for eight months, 
We have already checked almost all months tend is very  high with value of "0", so its indicate moreover people are paid very minimal amount with revolving credit


```{r}

names(bank_data1[6:11])
plot(bank_data1[6:11]) 
table(bank_data1$REPAY_SEP)
table(bank_data1$REPAY_AUG)
table(bank_data1$REPAY_JUL)
table(bank_data1$REPAY_JUN)
table(bank_data1$REPAY_MAY)
table(bank_data1$REPAY_APR)

```


```{r}
library(ggplot2)
# plotting scatter plot 
sepp <- ggplot(bank_data1, aes(x = PAID_AMT_SEP, y =BILL_AMT_SEP)) +  
  ylab("Bill outstanding  (NT$)") + geom_point() 
sepp + labs(x = "Last Payment (NT$)") + 
  labs(title="Scatter plot between Limit balance  And Payment of September")
```
#Important variables





#Creat dummy variables from REPAY_SEP to  REPAY_APR
-2 and -1 we have consiered here that customerare paid on time other than that all 0 to 8, we ahvecatogarized as late payer
```{r}
bank_data1$TIMELY_PD_SEP=ifelse(bank_data1$REPAY_SEP>0,0,1)
bank_data1$TIMELY_PD_AUG=ifelse(bank_data1$REPAY_AUG>0,0,1)
bank_data1$TIMELY_PD_JUL=ifelse(bank_data1$REPAY_JUL>0,0,1)
bank_data1$TIMELY_PD_JUN=ifelse(bank_data1$REPAY_JUN>0,0,1)
bank_data1$TIMELY_PD_MAY=ifelse(bank_data1$REPAY_MAY>0,0,1)
bank_data1$TIMELY_PD_APR=ifelse(bank_data1$REPAY_APR>0,0,1)
str(bank_data1)
```
#Checking the percentage of customers paid timely theri dues 
```{r}
table(bank_data1$TIMELY_PD_APR)
table(bank_data1$TIMELY_PD_MAY)
table(bank_data1$TIMELY_PD_JUN)
table(bank_data1$TIMELY_PD_JUL)
table(bank_data1$TIMELY_PD_AUG)
table(bank_data1$TIMELY_PD_SEP)
Per_Sep <- nrow(subset(bank_data1, TIMELY_PD_SEP == "0"))/nrow(bank_data1)
Per_Aug <- nrow(subset(bank_data1, TIMELY_PD_AUG == "0"))/nrow(bank_data1)
Per_Jul <- nrow(subset(bank_data1, TIMELY_PD_JUL == "0"))/nrow(bank_data1)
Per_Jun <- nrow(subset(bank_data1, TIMELY_PD_JUN == "0"))/nrow(bank_data1)
Per_May <- nrow(subset(bank_data1, TIMELY_PD_MAY == "0"))/nrow(bank_data1)
Per_Apr <- nrow(subset(bank_data1, TIMELY_PD_APR == "0"))/nrow(bank_data1)
Per_Sep
Per_Aug
Per_Jul
Per_Jun
Per_May
Per_Apr

```
we found in September22%,Auguest 14%, July 14%, June 11%, May 09 and April it is 10% customer are paid on time 

#Correlation between Variable
```{r}
#Checking umeric values 

names(bank_data1)
bank_data_num <- subset(bank_data1,select= -c(2,3,4))
numeric.list <- sapply(bank_data_num,is.numeric)
numeric.list
sum(numeric.list)
numeric.df1 <- bank_data_num[, numeric.list]

```

```{r}

cor.mat <- cor(numeric.df1)
cor.mat
```





```{r}
library(corrplot)
taiwan_bank1_matrix = cor(bank_data_num)
corrplot(taiwan_bank1_matrix, type="upper", method="number")

```

#KMO Test


```{r}
describe(bank_data1)
bank_data_cor <- subset(bank_data1, select = -c(1,2,3,4,5,24)) 
#is.na(bank_data1)
cormatrix_bank = cor(bank_data_cor)
library(psych)
cortest.bartlett(cormatrix_bank,100)
KMO(cormatrix_bank)
```
We have checked Kaiser-Meyer-Olkin (KMO) to find the Test for Sampling Adequacy whereas the values in  this case is greater than .5 , hence the data set is occurred with enough samples .


```{r}
#Check eigen values 
evector = eigen(cormatrix_bank)
eigen_value = evector$values
eigen_value
```


```{r}
plot(eigen_value, xlab = "Factors", ylab = "Eigen Values", col="red", pch=20)
lines(eigen_value, col="blue", lty = 2)
```
```{r}
fa1 = fa(r= bank_data_cor, nfactors =8, rotate ="none", fm ="pa")
print(fa1)
fa.diagram(fa1)

```
```{r}
fa2 = fa(r= bank_data_cor, nfactors = 8
         , rotate ="varimax", fm ="pa")
print(fa2)
fa.diagram(fa2)
```
#Renaming  vairbles
```{r}
bank_final <- subset(bank_data1,select = c(1,2,3,4,5,24))
bank_final_data = cbind(bank_final,fa2$scores)
head(bank_final_data)
colnames(bank_final_data) = c("LIMIT_BAL","SEX","EDUCATION","MARRIAGE","AGE","DEFAULT","BILLED _AMT",	"REPAY_STATUS ",	"PAID_AMT",	"TIMELY_PAID_AMT",	"RATIO_PADI_AMT1",	"RATIO_PADI_AMT2",	"RATIO_PADI_AMT3","RATIO_PADI_AMT4")
str(bank_final_data)
```

The variable we would be considering

# Check the proportion of data 
```{r}
### Check the proportion of data #
#Default payment in June, 2005 (1=yes, 0=no)
table(bank_final_data$DEFAULT)
nrow(subset(bank_final_data, DEFAULT == 1))/nrow(bank_final_data)

```

## Take the sample subset from the major class (here negative)
```{r}
set.seed(123)
train_idx <- sample(c(6:nrow(bank_final_data)), round(nrow(bank_final_data) * 0.7,0), replace = FALSE)
train_data <- bank_final_data[train_idx,]
test_data <- bank_final_data[-train_idx,]


table(train_data$DEFAULT)
table(test_data$DEFAULT)
```
## Checking the samples counts

```{r}
train.pos <- subset(train_data, DEFAULT == 1)
train.neg <- subset(train_data, DEFAULT == 0)

dim(train.pos)
dim(train.neg)

```

#Take the sample subset from the major class (here negative)
```{r}
## Set the seed
set.seed(108)  

train.neg.sub_idx <- sample(c(24:nrow(train.neg)), nrow(train.pos), replace = FALSE)
train_new <- train.neg[train.neg.sub_idx,]
dim(train_new)

```
# Merge the negative and positive cases 
```{r}

train_new <- rbind(train_new, train.pos) 
table(train_new$DEFAULT)

```

#Rendomizing  the data
```{r}

train_new <- train_new[sample(6:nrow(train_new)),]
### Now check the proportion of target in the sample
## in train_data
nrow(subset(train_data, DEFAULT == 1))/nrow(train_data)
## in train.new
nrow(subset(train_new, DEFAULT == 1))/nrow(train_new)
table(train_new$DEFAULT)
View(train_new)
```

```{r}
write.csv(train_new, file = "train_new.csv")
write.csv(test_data, file = "test_data.csv")
```

